---
title: "Small_Open_Economy_Model"
author: "Catarina Tavella"
date: "2022-09-06"
output:
  pdf_document:
    keep_tex: yes
    extra_dependencies: ["bbm", "amsmath"]
  html_document:
    df_print: paged
  word_document: default
geometry: left=1cm, right=1cm, top=1cm, bottom=1.5cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Problem of the consumer:

$\displaystyle \underset{C_t,N_t} {max} \ E_0 \sum_{t=0}^\infty \beta^tU(C_t,N_t) =                     \displaystyle \underset{C_{H,t},C_{F,t},N_t} {max} \ E_0 \sum_{t=0}^\infty \beta^tU \left(\left[ (1-\alpha)^{\frac{1}{\eta}} (C_{H,t})^{\frac{\eta-1}{\eta}} + \alpha^{\frac{1}{\eta}} (C_{F,t})^{\frac{\eta-1}{\eta}} \right]^{\frac{\eta}{\eta-1}},N_t \right)$ 

subject to the budget constraint (specified below), where 

$C_{H,t} \equiv \displaystyle \left( \int_0^1 C_{H,t}(j)^{\frac{\epsilon-1}{\epsilon}}dj \right) ^{\frac{\epsilon}{\epsilon-1}}$,  $C_{F,t} \equiv \displaystyle \left( \int_0^1 (C_{i,t})^{\frac{\gamma-1}{\gamma}}di \right) ^{\frac{\gamma}{\gamma-1}}$ and $C_{i,t} \equiv \displaystyle \left( \int_0^1 C_{i,t}(j)^{\frac{\epsilon-1}{\epsilon}}dj \right) ^{\frac{\epsilon}{\epsilon-1}}$

Substituting, we get

$\displaystyle \underset{C_{H,t},C_{F,t},N_t} {max} \ E_0 \sum_{t=0}^\infty \beta^tU \left(\left[ (1-\alpha)^{\frac{1}{\eta}} \left [\displaystyle \left( \int_0^1 C_{H,t}(j)^{\frac{\epsilon-1}{\epsilon}}dj \right) ^{\frac{\epsilon}{\epsilon-1}} \right]^{\frac{\eta-1}{\eta}} + \alpha^{\frac{1}{\eta}} \left[ \displaystyle \left( \int_0^1 (C_{F,t})^{\frac{\gamma-1}{\gamma}}di \right) ^{\frac{\gamma}{\gamma-1}} \right]^{\frac{\eta-1}{\eta}} \right]^{\frac{\eta}{\eta-1}},N_t \right)$ = 

$\displaystyle \underset{C_{H,t},C_{i,t},N_t} {max} \ E_0 \sum_{t=0}^\infty \beta^tU \left(\left[ (1-\alpha)^{\frac{1}{\eta}} \left [\displaystyle \left( \int_0^1 C_{H,t}(j)^{\frac{\epsilon-1}{\epsilon}}dj \right) ^{\frac{\epsilon}{\epsilon-1}} \right]^{\frac{\eta-1}{\eta}} + \alpha^{\frac{1}{\eta}} \left[ \displaystyle \left( \int_0^1 \left( \displaystyle \left( \int_0^1 C_{i,t}(j)^{\frac{\epsilon-1}{\epsilon}}dj \right) ^{\frac{\epsilon}{\epsilon-1}} \right)^{\frac{\gamma-1}{\gamma}}di \right) ^{\frac{\gamma}{\gamma-1}} \right]^{\frac{\eta-1}{\eta}} \right]^{\frac{\eta}{\eta-1}},N_t \right)$

subject to the budget constraint:

$\displaystyle \int_0^1 P_{H,t}(j)C_{H,t}(j)dj + \int_0^1\int_0^1 P_{i,t}(j)C_{i,t}(j)dj\ di + \mathbb{E}_t\{ Q_{t,t+1}D_{t+1}\} \leq D_t + W_tN_t + Tt$

As the budget constraint is binding, otherwise the consumer could spend more resources on more consumption and would not being optimizing his (or her consumption)

$\mathcal{L} = \displaystyle E_0 \sum_{t=0}^\infty \beta^t \left\lbrace U \left(\left[ (1-\alpha)^{\frac{1}{\eta}} \left [\displaystyle \left( \int_0^1 C_{H,t}(j)^{\frac{\epsilon-1}{\epsilon}}dj \right) ^{\frac{\epsilon}{\epsilon-1}} \right]^{\frac{\eta-1}{\eta}} + \alpha^{\frac{1}{\eta}} \left[ \displaystyle \left( \int_0^1 (C_{i,t})^{\frac{\gamma-1}{\gamma}}di \right) ^{\frac{\gamma}{\gamma-1}} \right]^{\frac{\eta-1}{\eta}} \right]^{\frac{\eta}{\eta-1}},N_t \right) + \\ \lambda_t \left(D_t + W_tN_t + Tt \displaystyle - \int_0^1 P_{H,t}(j)C_{H,t}(j)dj - \int_0^1\int_0^1 P_{i,t}(j)C_{i,t}(j)dj\ di - \mathbb{E}_t\{ Q_{t,t+1}D_{t+1}\}\right)  \right\rbrace$

The first order condition (FOC) for $C_{H,t}(j)$ is:

$\displaystyle U_c(C_t,N_t)\frac{\eta}{1-\eta}\left( C_t^{\frac{\eta-1}{\eta}} \right)^{\frac{\eta}{\eta-1}-1} (1-\alpha)^{\frac{1}{\eta}}\frac{\eta-1}{\eta}\left( C_{H,t}\right)^{-\frac{1}{\eta}}\frac{\epsilon}{\epsilon-1}\left(C_{H,t}^{\frac{\epsilon-1}{\epsilon}} \right)^{\frac{\epsilon}{\epsilon-1}-1}\int_0^1 \frac{\epsilon-1}{\epsilon} C_{H,t}(j)^{-\frac{1}{\epsilon}}dj = \lambda_t \int_0^1 P_{H,t}(j)dj$

 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
